```{r, echo=FALSE}
knitr::opts_chunk$set(error = TRUE)
```

---
title: "DPLYR"
author: "William Taylor Bickelmann"
date: "September 1, 2017"
output: html_document
---

For this page I will be doing some very basic data manipulation using the packages SQLDF and DPLYR. 
##Filtering columns and rows
(had to use sqldf becuase dplyr was acting wonky)
sqldf allows one to use standard query language sytanx to pull data from dataframes.
with this I queried the Batting table in the Lahman package


```{r}
sqldf("select playerID, yearID, teamID, HR 
      from Batting
      WHERE teamID == 'NYA' and yearID == 1927")
```

Here some code that selects and summarizes the number of people from the New York Yankees who had over 40 homeruns. This code,unlike the code above was done in DPLYR; a package made by Hadley Wickam.

```{r}
Batting%>%
  select(HR, teamID, playerID)%>%
  filter(HR >=40 & teamID=="NYA")%>%
  summarise(cnt=n())
```

Now to add some code which return the same results but in a different order

```{r}
Batting%>%
  filter(HR>=40, teamID=="NYA")%>%
  select(playerID,yearID,teamID,HR)
```

Next, I will add some code to add selecting players with at least 40 homeruns and under 60 strike outs

```{r}
Batting%>%
  select(playerID,yearID,teamID,HR,SO)%>%
  filter(HR >= 40, SO<60)
```
Now I am going to add code to select players with over 30 homeruns for a different team between 1979 and 1970

```{r}
Batting%>%
  select(playerID,yearID,teamID,HR)%>%
  filter(teamID =="PHI", HR>30, yearID<=1979, yearID>=1970)
```


now for code selecting players with over 50 homeruns with the players with the most homeruns sorted first
```{r}

Batting%>%
  select(HR, playerID, yearID)%>%
  filter(HR > 50)%>%
  arrange(desc(HR))
```


My code is poetry. Watch me go

```{r}
Batting%>%
  select(playerID, SO, AB)%>%
  filter(AB>=400, SO<10)%>%
  arrange(SO)%>%
  summarise(cnt=n(), average_AB = mean(AB))
```
```{r}
Batting%>%
  filter(playerID =="ruthba01")%>%
  group_by(playerID)%>%
  summarise(career_HR=sum(HR))
```

```{r}
Batting%>%
  select(playerID, HR)%>%
  group_by(playerID)%>%
  summarize(career_HR=sum(HR))%>%
  filter(career_HR > 600)%>%
  arrange(desc(career_HR))
```
```{r}
Batting%>%
  select(playerID, HR)%>%
  group_by(playerID)%>%
  summarize(average=mean(HR))%>%
  filter(average>20)%>%
  arrange(desc(average))%>%
  summarize(cnt=n())
```

```{r}
Batting%>%
  select(playerID, HR, yearID)%>%
  filter(yearID>1970, HR>50)%>%
  group_by(playerID)%>%
  distinct(playerID)
```

